The resurgence of the linear optics interferometer --- recent advances \& applications

### 2017-05-13 paper.tex
Revised intro

\begin{abstract}
%%%
Linear optics has seen a resurgence owing to its miniaturisation on-chip, and increase in production efficiency and quality of single photons. Time-bin encodings have also become feasible owing to fresh architecture, and processing capabilities. Theoretical efforts to find useful application beyond a full universal quantum computation has also bore fruit. A sampling task, known as {\sc bosonsampling} that is easily implemented using linear optics but is strongly believed to be a hard for a classical computer, has emerged. 
%%%%
\end{abstract}

@@

Technical advancements in linear optics have been made on many fronts that make it increasingly attractive for quantum computing applications. It is possible now to put single-photon sources and detectors together with linear-optical networks on a silica chip. The advantage of using such integrated photonics over bulk optics is that it is more stable against phase fluctuations, and miniaturized. This increases the scalability of optical implementations of quantum information protocols. Having all components on chip reduces coupling losses which would be crucial for fault-tolerance. An optical implementation of quantum protocols can potentially piggyback on existing communication infrastructure. Combined withthe relative ease of transporting quantum states of light, as compared to say trapped ions or superconducting qubits, linear optics forms a powerful platform for quantum information processing.

@@

An EPR pair, or Bell pair, is one of the four states,
\begin{align}
\ket{0}_A\ket{0}_B &\pm \ket{1}_A\ket{1}_B, \nonumber \ {\rm and} \\
\ket{1}_A\ket{0}_B &\pm \ket{0}_A\ket{1}_B,
\end{align}
which are all maximally entangled and locally equivalent to one another. These are the simplest examples of entangled states, and their preparation via SPDC has been the mainstay of entangled state preparation for quantum optical processing.
%\cite{bib:Kim01,bib:Kim03,bib:Brida07,bib:Dayan07}.
In some applications, it may be desired to have the EPR pairs conditionally prepared, {\it i.e.~}successfully prepared only under certain measurement outcomes of auxiliary modes. Several theoretical approaches have been proposed for this purpose \cite{bib:Pittman03,bib:Sliwa03,bib:Walther07}, and demonstrated \cite{bib:Wagenknecht10,bib:Barz10}.

@@

 Integrated photonic circuits has greatly improved the feasibility of LOQC. Their small size and interferometric stability enable the requisite quantum interference to happen in certain LOQC settings. Programmable circuits that are reusable have also emerged \cite{bib:Metcalf14,bib:Carolan15}. This saves resources and lead time for producing new circuits. Combining these chips with existing higher-efficiency sources and detectors will expand their capabilities. Loss can be mitigated by moving all components onto the same chip as the linear optical circuit \cite{bib:Sprengers11, bib:Silverstone14}.  What remains is to have fast feedforward also on chip. This might pose the greatest challenge yet for universal LOQC. The bottleneck is in the speed of modulation in the feedforward circuitry; only a handful of experiments have been able to implement adaptive feedforward for the purposes of LOQC \cite{bib:Prevedel07,bib:Xiao-Song12,bib:Mikova12,bib:Zhao14}.

>>>>

\begin{abstract}
%%%
Linear optics has seen a resurgence for applications in quantum information processing owing to its miniaturisation on-chip, and increase in production efficiency and quality of single photons. Time-bin encodings have also become feasible owing to architectural breakthroughs, and new processing capabilities. Theoretical efforts have found new ways to implement universal quantum computations with linear optics requiring less resources, and to demonstrate the capabilities of linear optics without requiring a universal optical quantum computer.%%%%
\end{abstract}

@@

Linear optics play a prominent role in quantum information processing. Photons make fantastic ``flying" qubits, and are readily used for quantum communication \cite{bib:Northup14} and quantum key distribution \cite{bib:Lo14}. In 2001, Knill, Laflamme and Milburn showed that efficient quantum computing is possible using only linear optical components, that is single photons, beamsplitters, phase shifters and photon counting \cite{bib:KLM01}. Furthermore, an optical implementation of quantum protocols can potentially piggyback on existing communication infrastructure. Combined with the relative ease of transporting quantum states of light, as compared to say trapped ions or superconducting qubits, linear optics forms a powerful platform for quantum information processing.

The promises offered by linear optics have spearheaded many technical advancements. One of the major successes for linear optics is the paradigm shift from bulk optics to integrated photonics \cite{bib:Meany15}. The advantage of using such integrated photonics over bulk optics is that it is more stable against phase fluctuations, and miniaturized. This has increased the scalability of optical implementations of quantum information protocols. Furthermore, it is now possible to have single-photon sources and detectors together with linear-optical networks on a silica chip \cite{bib:Sprengers11, bib:Silverstone14}. Having all components on chip reduces coupling losses which would be crucial for fault-tolerance \cite{bib:Li15}.

@@

An EPR pair, or Bell pair, is one of the four states,
\begin{align}
\ket{0}_A\ket{0}_B &\pm \ket{1}_A\ket{1}_B, \nonumber \ {\rm and} \\
\ket{1}_A\ket{0}_B &\pm \ket{0}_A\ket{1}_B,
\end{align}
which are all maximally entangled and locally equivalent to one another. These are the simplest examples of entangled states, and their preparation via SPDC has been the mainstay of entangled state preparation for quantum optical processing \cite{bib:Kim01}.
%\cite{bib:Kim01,bib:Kim03,bib:Brida07,bib:Dayan07}.
In some applications, it may be desired to have the EPR pairs conditionally prepared, {\it i.e.~}successfully prepared only under certain measurement outcomes of auxiliary modes. Because the EPR qubits are not measured directly, they can be used subsequently. Several theoretical approaches have been proposed for this purpose \cite{bib:Pittman03,bib:Sliwa03,bib:Walther07}, and demonstrated \cite{bib:Wagenknecht10,bib:Barz10}.

@@

 Integrated photonic circuits has greatly improved the feasibility of LOQC. Their small size and interferometric stability enable the requisite quantum interference to happen in certain LOQC settings. Programmable circuits that are reusable have also emerged \cite{bib:Metcalf14,bib:Carolan15}. This saves resources and lead time for producing new circuits. Combining these chips with existing higher-efficiency sources and detectors will expand their capabilities. Loss can be mitigated by moving all components, {\it i.e.~}sources and detectors, onto the same chip as the linear optical circuit \cite{bib:Sprengers11, bib:Silverstone14}.  What remains is to have fast feedforward also on chip. This might pose the greatest challenge yet for universal LOQC. The bottleneck is in the speed of modulation in the feedforward circuitry; only a handful of experiments have been able to implement adaptive feedforward for the purposes of LOQC \cite{bib:Prevedel07,bib:Xiao-Song12,bib:Mikova12,bib:Zhao14}.
